On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Mv 150914PE cite before extreme spin statment [33]

In the context of \gw{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.

>>>>

In the context of \gw{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins \cite{TheLIGOScientific:2016wfe}, it is useful to have accurate physical behavior in the extremal limit.
